---
title: "Final Project Proposal"
author: "Daniel Dittenhafer & Justin Hink"
date: "December 5, 2016"
documentclass: article 
geometry: margin=0.75in
output: 
  pdf_document:
    number_sections: yes
subtitle: "DATA620: Web Analytics"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(knitcitations)
library(RefManageR)

cleanbib()

cite_options(style="markdown")

nbcTrumpCabinet <- bibentry(bibtype="Misc",
                         author=person(family="Rafferty", first="Andrew"),
                         publisher="NBC News",
                         title="Donald Trump's Cabinet Picks So Far",
                         year=2016,
                         month="December",
                         url="http://www.nbcnews.com/politics/politics-news/donald-trump-s-cabinet-picks-so-far-n690296")

```

# Problem Statement & Research Questions

We are interested in analyzing President-elect Trump's Cabinet nominations from a social and graph analytics perspective. 

# Statement of Objectives

Using graph and text analytics, we will explore the individuals whom have been (or are expected to be) nominated for
positions in President-elect Donald Trump's cabinet.

# Data Set

The data set is derived from an article written by Andrew Raffery and published by NBC News `r citep(nbcTrumpCabinet)`. We plan to augment this data set with web-based data including Wikipedia articles about each
of the nominees.


# Evaluation

TBD

# References

```{r, results='asis', echo=FALSE}
BibOptions(style="html", bib.style="authortitle")
bibliography()
```
