---
title: "Final Project Proposal"
author: "Daniel Dittenhafer & Justin Hink"
date: "December 11, 2016"
output:
  pdf_document:
    number_sections: yes
  html_document: default
geometry: margin=0.75in
subtitle: 'DATA620: Web Analytics'
documentclass: article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(knitcitations)
library(RefManageR)

cleanbib()

cite_options(style="markdown")

nbcTrumpCabinet <- bibentry(bibtype="Misc",
                         author=person(family="Rafferty", first="Andrew"),
                         publisher="NBC News",
                         title="Donald Trump's Cabinet Picks So Far",
                         year=2016,
                         month="December",
                         url="http://www.nbcnews.com/politics/politics-news/donald-trump-s-cabinet-picks-so-far-n690296")

```

# Problem Statement & Research Questions

For the project we will analyze President-elect Trump's Cabinet nominations from a social and graph analytics perspective.  We will look at the network of relationships between the individuals as well as the organizations in which they play a prominent role.  

Additionally, we will attempt to unearth common themes in the descriptions of the above described entites from a textual analysis of the currated descriptions of them on Wikipedia. 

# Statement of Objectives

Using graph and text analytics, we will explore the individuals whom have been (or are expected to be) nominated for
positions in President-elect Donald Trump's cabinet.  Note: Since a number of these positions have yet to be finalized, these data are changing quite frequently.  The project will be completed with data current as of 12/11/2016

# Data Set

The data set is derived from an article written by Andrew Raffery and published by NBC News `r citep(nbcTrumpCabinet)`. We plan to augment this data set with web-based data including Wikipedia articles about each of the nominees and their organizations.


# Evaluation

## Graph Analysis:

Basic graph analysis metrics will be extracted along with visualizations of the following categories:

* Prior Organization
* Prior Organization Type
* Prior Position / Title


##Text Analysis:

- A custom library will be written that scrapes raw wikipedia content and converts it into a visual display of the most commonly used words (known olloquially as a word cloud)
- Will leverage python packages: 'BeautifulSoup' and 'wordcloud' 
- The accumulated text will be aggregated and analyzed for general language patterns (common metric such as Zipf's law)

# References

```{r, results='asis', echo=FALSE}
BibOptions(style="html", bib.style="authortitle")
bibliography()
```
